Visual Question Answering with DeepProbLog

### 2022-03-09 paper/paper.tex
Add the first writings for the paper

\title{ENGLISH GUIDELINES FOR PUBLICATION - TITLE HERE \\(14 PT TYPE SIZE, UPPERCASE, BOLD, CENTERED)}

\author{First A. Author$^{1}$, Second B. Author$^{2}$ (Authors' Names, 12 pt Type Size, Centered Under the Title)\\
	\normalsize $^{1}$First Affiliation, City -- State, Country (10 pt Type Size, Centered Under the Authors' Names)\\
	\normalsize $^{2}$Second Affiliation (if necessary), City -- State, Country (10 pt Type Size, Centered Under the Authors' Names)\\
	\normalsize e-mail: author1@email.br, author2@email.com
}

@@

\begin{abstract}
	The objective of this document is to instruct the authors about the preparation of the manuscript for its submission to the Revista Eletrônica de Potência (Brazilian Power Electronics Journal).~The authors should use these guidelines for preparing both the initial and final versions of their paper. Additional information about procedures and guidelines for publication can be obtained directly with the editor, or through the web site https://mc04.manuscriptcentral.com/revistaep. This text was written according to these guidelines.
\end{abstract}

\begin{keywords}
	Authors shall provide a maximum of six keywords (in alphabetical order, capitalized, separated by commas) to help identify the major topics of the paper.
\end{keywords}

\let\thefootnote\relax\footnotetext{\hspace*{-5mm}This footnote will be used only by the Editor and Associate Editors.~The edition in this area is not permitted to the authors. This footnote must not be removed while editing the manuscript.}

\section*{NOMENCLATURE}

\symbolnomenclature{$P$}{Number of poles.}
\symbolnomenclature{$V_{qd}$}{Stator voltage \textit{dq} components.}
\symbolnomenclature{$I_{qd}$}{Stator current \textit{dq} components.}

@@

\section{INTRODUCTION}

The Brazilian Power Electronics Journal (Revista Eletrônica de Potência) is an appropriate media through which the SOBRAEP (Brazilian Power Electronics Society) members and experts in the field of Power Electronics may present and discuss their scientific and academic activities. Therefore, the Editorial Staff invites you to submit a full format paper in the field of Power Electronics, including advances in the state of the art, through theoretical and experimental results, as well as tutorial information on subjects of interest to the Society. In case the paper, or part of it, has been presented or published in any national or international journal or conference, it must be declared by the authors in the body of the paper (when and where).

Papers in Portuguese and English will be accepted. The texts submitted in Portuguese must include the title, the abstract and the keywords in English as well.

Authors must submit their manuscript electronically and follow the revision process through the https://mc04.manuscriptcentral.com/revistaep.~From this entry page, access can be obtained to all information required for the submission of a manuscript.

It should be noted that manuscripts must be submitted as an editable PDF document. Therefore, after editing your manuscript in agreement with these guidelines, a high-quality PDF file must be generated so it can be submitted through the https://mc04.manuscriptcentral.com/revistaep. Upon Final Acceptance of the manuscript, the strong requirement for publication is a final electronic version of the paper prepared in agreement with these guidelines. In addition, papers will only be published if the Copyright form available at the https://mc04.manuscriptcentral.com/revistaep is completed.

The main objective of the Introduction section is presenting the nature of the problem that is discussed in the paper, through an adequate literature review, and the contribution of the submitted manuscript.

If relevant, a Nomenclature section may be included immediately before the Introduction, with a list of variables used in the text. This item should not contain reference numeration, as well as items Acknowledgements, References and Biographies.

@@

At the end of these guidelines, there is an example of how the references should be inserted~\cite{refbib1,refbib2,refbib3,refbib4,refbib5,refbib6,refbib7,refbib8}.

@@

\begin{figure}[H]
	\includegraphics[scale=1]{figura.eps}
	\centering
	\caption{Magnetization as a function of applied field. (Note that ``Fig.'' is abbreviated and there is a period after the figure number followed by two spaces.)}
	\label{fig:fig1}
\end{figure}

>>>>

\title{Visual Question Answering with DeepProbLog}

\author{Jorrit Willaert$^{1}$ \\
	\normalsize $^{1}$Catholic University of Leuven, Leuven -- Belgium \\
	\normalsize e-mail: jorrit.willaert@student.kuleuven.be
}

@@

\begin{abstract}
	TODO
\end{abstract}

\begin{keywords}
	Neuro Symbolic AI, Visual Question Answering, DeepProbLog, Problog, Convolutional Neural Networks
\end{keywords}

%\let\thefootnote\relax\footnotetext{\hspace*{-5mm}This footnote will be used only by the Editor and Associate Editors.~The edition in this area is not permitted to the authors. This footnote must not be removed while editing the manuscript.}

%\section*{NOMENCLATURE}

%\symbolnomenclature{$P$}{Number of poles.}
%\symbolnomenclature{$V_{qd}$}{Stator voltage \textit{dq} components.}
%\symbolnomenclature{$I_{qd}$}{Stator current \textit{dq} components.}

@@

\section{INTRODUCTION}
The Neuro Symbolic AI community is growing rapidly, indicating that people start to recognize the value of the field. The Neuro Symbolic AI field is interested in building a bridge between the robustness of probabilistic knowledge, with the well-known popularity and proven strengths of deep neural networks. DeepProbLog offers this ability, by using both the strengths of neural networks (i.e. system 1, typical subconscious tasks such as visual recognition, the processing of languages, \dots), along with the strengths of rule-based probabilistic systems (i.e. system 2, slow, sequential thinking such as the derivation of a proof).

This paper elaborates on an application that requires both systems to be used, namely Visual Question Answering. System 1 will be required in order to gain an understanding of the image under investigation, with in particular their shapes and colors. System 2, on the other hand, will use this extracted information for deriving certain properties of objects\footnote{For example, finding the shape of the green object, or deriving if it is located on the left hand side of the image.}, or even for capturing the relations\footnote{Here, one could think of deriving if an object is located to the left of another object, or also for finding the number of circles in the image.} between the objects.

@@

At the end of these guidelines, there is an example of how the references should be inserted~%\cite{refbib1,refbib2,refbib3,refbib4,refbib5,refbib6,refbib7,refbib8}.

@@

\begin{figure}[H]
%	\includegraphics[scale=1]{figura.eps}
	\centering
	\caption{Magnetization as a function of applied field. (Note that ``Fig.'' is abbreviated and there is a period after the figure number followed by two spaces.)}
	\label{fig:fig1}
\end{figure}
